---
title: "Web App"
format: html
editor: source
engine: knitr
---

Keeping track of apquarto's many options can be difficult, and with each new feature, the list of options grows. I have make a small app that makes it easier to create the initial apaquarto document. Because this app runs locally on your machine, your data stays private. 

The app requires that the [shiny package](https://shiny.posit.co/r/getstarted/shiny-basics/lesson1/) is installed. If needed, install shiny by running this code in your R console first:

```{r installshiny, eval=FALSE, echo=TRUE}
install.packages(shiny)
```


When ready, start the app by running this code in your R console:


```{r runshiny, eval=FALSE, echo=TRUE}
shiny::runGitHub(repo = "apa7maker", username = "wjschne")
```

The app is mostly self-explanatory. You fill in necessary information or select options that suit your purpose. When ready, click `Make Document` in the side menu and then click `Update`. Either copy the resulting text into an existing Quarto file, or download the file to a directory of your choice.