---
title: "Template Options"
toc: true
# The option lists are written from options.yml when the page renders.
# Frozen, an edit to options.yml alone would never reach the page.
execute:
  freeze: false
---

```{r}
#| include: false
source("options-helpers.R")
```

Options are set in the metadata section at the top of the .qmd file. Quarto metadata uses [YAML](https://yaml.org/), a format that allows us to store data in a format that is easy to write and easy to read. In its simplest form, it has a key and a value:

``` yaml
key: value
```

If the value is simple, it does not need any quotes. If it has any characters that have special meaning in yaml (e.g., `:`), you will need to put the value in quotes.

``` yaml
title: "This title needs quotes: Because there is a colon in it."
```

Any optional key you do not use can be deleted or commented out. If you would prefer to keep the key visible but empty, you can make the value `NULL` with the tilde symbol `~` like so:

``` yaml
key: ~
```

If you want the null value to be easier to understand, you can specify a null value explicitly:

``` yaml
key: null
```

Here is a minimal example of what the YAML metadata might look like:

``` yaml
---
title: "My Paper's Title: A Full Analysis of Everything"
shorttitle: "My Paper's Title"
author:
  - name: W. Joel Schneider
    corresponding: true
    orcid: 0000-0002-8393-5316
    email: schneider@temple.edu
    affiliations:
      - name: Temple University
        department: College of Education and Human Development
        address: 358 Ritter Hall
        city: Philadelphia
        region: PA
        postal-code: 19122-6091
abstract: "This is my abstract."
keywords: [keyword1, keyword2]
author-note:
  disclosures:
    conflict of interest: The author has no conflict of interest to declare.
bibliography: mybibfile.bib     
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-pdf: default
  apaquarto-typst: default
---
```

# General Options

```{r}
#| echo: false
#| results: asis
apa_options("general")
```

## Authors

The apaquarto uses the [standard Quarto schema for authors](https://quarto.org/docs/authoring/front-matter.html#author). It has a lot of options, some of which are not needed for the apaquarto extension (e.g., `fax`, `phone`, `degrees`, `note`, `acknowledgements`).

The `author` field contains author names, author affiliations, and author roles. Where possible, specify each author's [orcid](https://orcid.org/) for easy, unambiguous identification.

The corresponding author is specified by setting the author's corresponding field to true (i.e., `corresponding: true`). This author needs to list an email and list a mailing address in the affiliation data. Only one author can be the corresponding author. Other authors do not need to list their addresses.

``` yaml
author:
  - name: W. Joel Schneider
    corresponding: true
    orcid: 0000-0002-8393-5316
    email: schneider@temple.edu
    affiliations:
      - name: Temple University
        department: College of Education and Human Development
        address: 1301 Cecil B. Moore Ave.
        city: Philadelphia
        region: PA
        postal-code: 19122-6091
    role:
      - writing
      - conceptualization
  - name: Fulano Zutano Mengano
    affiliations: Universidad de Dondequiera
    orcid: 0000-0000-0000-0001
    role:
      - formal analysis
      - visualization
      - editing
  - name: Thomas Richard Harris
    affiliations: 
      - name: Generic State University
        department: Department of Scholarly Studies
    orcid: 0000-0000-0000-0002
    role:
      - editing
      - funding acquisition
  - name: Wut C. Whosis
    affiliations: Whatchama College
    orcid: 0000-0000-0000-0003
    role:
      - software
      - methodology
      - editing
```

## Affiliations

The apaquarto extension uses the [standard Quarto schema for affiliations](https://quarto.org/docs/journals/authors.html#affiliations-schema).

```{r}
#| echo: false
#| results: asis
apa_options("affiliations")
```

### Multiple Affiliations

If an author has more than one affiliation:

``` yaml
author:
  - name: William Joel Schneider
    affiliations:
      - name: Temple University
        department: College of Education and Human Development
        address: 1301 Cecil B. Moore Ave.
        city: Philadelphia
        region: PA
        postal-code: 19122-6091
      - name: My Second Affiliation
```

### Shared Affiliations

If two authors have the same affiliation, you can type the same affiliation twice. If you do this, make sure the affiliations are EXACTLY the same in every detail. Otherwise they will be listed as different. To make sure they are listed as the same affiliation, it is safer to use a reference id to make sure that there are no accidental differences that creep in to the editing process. In this example, the affiliation information was entered once, and the `id` was specified. For the second author with the same affiliation, the `ref` field is used to reference the previously specified `id`.

``` yaml
author:
  - name: William Joel Schneider
    affiliations:
      - name: Temple University
        department: College of Education and Human Development
        address: 1301 Cecil B. Moore Ave.
        city: Philadelphia
        region: PA
        postal-code: 19122-6091
        id: temple
  - name: Renée M. Tobin
    affiliations:
      - ref: temple
```

### Listing Authors and Affiliations Separately

If there are a lot of authors with shared affiliations, it might be easier to list the affiliations separately and specify each affiliation's `id`, which can be looked up with the `ref` field:

``` yaml
author: 
  - name: Fred Jones
    affiliation: 
      - ref: temple
      - ref: tamu
  - name: Wanda James
    affiliation:
      - ref: temple
      - ref: ucb
affiliations:
  - id: temple
    name: Temple University
  - id: tamu
    name: "Texas A&M University"
  - id: ucb
    name: University of California, Berkeley
```

## Author Roles

APA Style encourages but does not require papers with multiple authors to describe author roles using the [Contributor Roles Taxonomy](https://credit.niso.org/) (CRediT). There are 14 contributor roles:

```{r}
#| echo: false
#| results: asis
apa_options("author-roles")
```

It is possible to list the roles for each author:

``` yaml
author: 
  - name: Fred Jones
    role: 
      - conceptualization
      - funding acquisition
      - writing
  - name: Wanda James
    role:
      - conceptualization
      - formal analysis
      - visualization
      - editing
```

When 2 or more authors have the same role, one may specify the degree of contribution (`lead`, `equal`, `supporting`):

``` yaml
author: 
  - name: Fred Jones
    role: 
      - conceptualization: lead
      - visualization: supporting
      - investigation: equal
      - funding acquisition
      - writing
  - name: Wanda James
    role:
      - conceptualization: supporting
      - visualization: lead
      - investigation: equal
      - formal analysis
      - editing
```

## Author Notes

The first paragraph of the Author Note will be populated with all the ORCID IDs that have been specified.

The second paragraph consists of status changes:

```{r}
#| echo: false
#| results: asis
apa_options("author-note-status")
```

The third paragraph consists of study details and author disclosures:

```{r}
#| echo: false
#| results: asis
apa_options("author-note-disclosures")
```

The fourth paragraph of the Author Note consists of the correspondence information. It will created automatically from the contact information from the author marked as the corresponding author. If you wish to override this paragraph with one entirely of your own, you can set it via the `correspondence-note` subfield in the `author-note` field.

``` yaml
author-note:
  correspondence-note: This will override the correspondence note that would otherwise be generated.
```

# Options for .docx and typst

```{r}
#| echo: false
#| results: asis
apa_options("docx-typst")
```

# Options for .pdf

As of 6.0.0 the .pdf is set in plain $\LaTeX$ rather than with the apa7 class, so these are apaquarto's own options and no longer those of [apa7](https://ctan.org/pkg/apa7?lang=en). Four fields that belonged to that class --- `donotrepeattitle`, `draftfirst`, `draftall` and `nocorrespondence` --- no longer do anything; the first has become `suppress-title-introduction` and the last `suppress-corresponding-paragraph`, both of which work in every format. A document's own yaml is otherwise unchanged.

```{r}
#| echo: false
#| results: asis
apa_options("pdf")
```

# Document modes in pdf and typst

The `documentmode` field works in `apaquarto-typst` as well as `apaquarto-pdf`. All four modes are supported: `man` (manuscript), `jou` (journal, two columns), `doc` (a plain continuous document), and `stu` (student paper). In both formats each mode may also be named in full: `journal`, `manuscript`, `document`, and `student` are accepted as aliases for `jou`, `man`, `doc`, and `stu`.

In `stu` mode the student-paper fields `course`, `professor`, `duedate`, and `note` are placed on the title page.

In `jou` mode the journal metadata is set as a masthead at the head of the first page, the way the journals set one: the journal's name at the right with its logo opposite, a rule under both, and the issue on the right beneath it with the copyright on the left. All of it goes under `journal`, which Quarto reserves as an object:

``` yaml
journal:
  title: "Journal of Educational Psychology"
  logo: apa-logo.png
  year: 2026
  volume: 118
  issue: 6
  pages: 869--888
  url: "https://doi.org/10.1037/edu0000976"
  issn: 0022-0663
  copyrightnotice: 2025
  copyrighttext: "The Author(s)"
```

which is set as

+----------------------------------+------------------------------------+
|                                  |                                    |
+:=================================+===================================:+
| *logo*                           | Journal of Educational Psychology  |
+----------------------------------+------------------------------------+
| © 2025 The Author(s)             | 2026, Vol. 118, No. 6, 869--888    |
+----------------------------------+------------------------------------+
| ISSN: 0022-0663                  | https://doi.org/10.1037/edu0000976 |
+----------------------------------+------------------------------------+

`logo` is a path to an image file, read the same way a path in the document is. Writing `logo: default` instead of a path uses the apaquarto logo, which the extension ships with, so that a masthead can be seen without one having to be found first.

Every field is optional, and anything left out is simply left out: a `journal` with nothing but a `title` gives the name and the rule and no more. The words "Vol." and "No." can be changed with `journal-volume` and `journal-issue` in the `language` field.

# Dissertations and Theses

`documentmode: thesis` sets a dissertation or thesis for the Temple
University Graduate School, following its
[Dissertation and Thesis Handbook](https://grad.temple.edu/sites/grad/files/media/document/Dissertation%20and%20Thesis%20Handbook%202024-2025%20(1).pdf).
It is manuscript mode with a front matter of its own, and it works in all
four formats. `dissertation` is accepted as an alias.

The front matter is built for you, in the order the handbook sets it: title,
copyright, abstract, dedication, acknowledgments, table of contents, and a
list for each kind of float the document holds. Each page is left out when
the document gives it nothing to set, and the numbering runs on over whatever
is there.

The page takes its fields from a `thesis` block:

``` yaml
documentmode: thesis
thesis:
  type: Dissertation
  submitted-to: the Temple University Graduate Board
  degree: Doctor of Philosophy
  date: May 2027
  committee:
    - name: Mentor's Name
      role: Advisory Chair
      affiliation: TU Department
    - name: Committee Member's Name
      affiliation: TU Department
    - name: Committee Member's Name
      role: External Member
      affiliation: Another University
```

```{r}
#| echo: false
#| results: asis
apa_options("thesis")
```

Every field is optional: a block left out leaves its part of the page out,
and the rule that sets it off goes with it.

The author is the document's own `author`, and the title its own `title`.

## The shape of the title

The Graduate School asks for the title in capitals, and for an inverted
pyramid when it runs to more than one line: the first line longest, each line
after it shorter. apaquarto works the lines out for you. It measures the
words and tries every arrangement from two lines up to eight, aiming each
line at a straight taper --- for a title of four lines, the full measure,
three quarters of it, half, a quarter --- and takes the arrangement that sits
nearest. That settles how many lines the title wants without anyone having to
say.

The lines are worked out once, in Lua, and handed to all four formats, so the
title page has the same shape in the .pdf, the .docx, the typst and the
.html.

To break the title yourself instead, write it as a block and end each line
with a backslash:

``` yaml
title: |
  This is the First Line of My Title \
  And This is the Second Line
```

Those are then the lines, and nothing is worked out.

## Margins

The handbook asks for 1.5" at the left, where the work is bound, and 1"
elsewhere, and says the margins are "the same for the entire manuscript,
including front matter". `documentmode: thesis` sets them in the .pdf, the
typst and the .docx.

A margin the document names with `margin` replaces the handbook's on every
page but the title page, the front matter as well as the body, so the whole
work moves together, in all three formats. A side left out keeps the
handbook's.

``` yaml
margin:
  left: 1.25in
```

The title page is the exception: it is set on 1" all round, so that the block
of it stands at the centre of the paper rather than at the centre of a text
block pushed right by the binding margin. That is what the dissertations
Temple publishes do, and what the Graduate School's own template draws. The
title is broken against the measure that page has, not the body's.
`title-margin` under `thesis` gives it margins of its own.

Confirm with the Graduate School before submitting on margins other than the
handbook's.

## The abstract, the dedication and the acknowledgments

The abstract is the document's own `abstract`, and the acknowledgments are
`acknowledgments` (or `acknowledgements`). Each is set under a heading of its
own, in capitals and centred, with the prose flush at the margin, no first
line indented, and double spaced, as the handbook asks. Either runs as long
as it runs and takes a second page if it needs one.

The dedication is `dedication`. It carries no heading and is centred, double
spaced, well down its own page.

All three may be written at the top level, beside `abstract`, or inside the
`thesis` block.

``` yaml
abstract: "What the work found."
dedication: |
  For everyone who wondered whether this would ever be finished.
acknowledgments: |
  Thanks to my committee, and to everyone who read a draft.
```

The Graduate School's own template sets its abstract and its acknowledgments
differently from one another --- one begins at the margin and the other is
indented, and the air under the heading is not the same on both. apaquarto
sets them alike.

## The table of contents

The contents lists the front matter in capitals --- the abstract, the
dedication, the acknowledgments --- then the chapters under a column label
reading `CHAPTER`, each with its arabic number and its title in capitals, and
then the back matter: the references, and the appendices, lettered in the
order they are mentioned. `Page` stands at the right margin under the
heading, and leader dots run out to the page numbers.

Neither the copyright page nor the contents itself is listed, which is what
the handbook asks. `CHAPTER` and `APPENDICES` are column labels rather than
entries: they carry no leader and no page, and the chapters and appendices
under them carry both.

The entries are black. They are links, and a link would otherwise take
`linkcolor` and leave the contents reading as a page of cross references
rather than as a list; `toccolor` says what they take instead, in the lists
of tables and figures as well.

How deep it goes is quarto's own `toc-depth`, counting levels of heading:
`1` lists the chapters and nothing under them, `4` adds the three levels of
subheading the handbook allows, and anything deeper is cut back to four.
Quarto's default is `3`.

``` yaml
toc-depth: 1
```

The handbook asks that a level listed for one chapter be listed for every
chapter that has it, which is worth a look before you go deeper than the
chapters.

## Chapters

A chapter is a level-one heading in the body. In thesis mode a heading
reading *Introduction* at the head of the body is kept rather than taken out
--- a dissertation's chapters are named, and that heading is the first
chapter's name.

Every level-one heading is set in capitals, and over each chapter stands the
word `CHAPTER` and its number, on a line of its own and set like the heading
under it.

Every major division begins a page of its own, which is what the handbook
asks: each chapter, the references, and each appendix.

A level-one heading with a part of its own to play --- the references, an
appendix, the label over an appendix --- is not a chapter. It is set in
capitals like the rest but carries no `CHAPTER` line and is not counted in
the numbering.

The `CHAPTER` lines are not listed in the table of contents, which names a
chapter by its own heading. The word can be changed with
`thesis-chapter-label` in the `language` field.

In the .pdf and in typst the page numbers are worked out as the document is
set. In .docx they are fields, as the lists of figures and tables are, and
they are blank until something makes Word paginate: select all and press
<kbd>F9</kbd>, or print, or export to PDF. .html has no pages, so an entry
there is the words and a link to them.

## The lists of tables, figures and illustrations

A dissertation carries a table of contents and a list for each kind of float
unless it says otherwise, which is the other way round from apaquarto's other
modes: `list-of-contents`, `list-of-tables`, `list-of-figures` and
`list-of-illustrations` are all true here, and the field says what to leave
out rather than what to put in.

``` yaml
list-of-illustrations: false
```

A list with nothing in it is left out whatever the field says, and the
contents does not name it: a heading reading `LIST OF TABLES` over an empty
page helps nobody, and the Graduate School's own template says as much ---
"if no tables, delete this page".

A list is built for every kind of float the document holds --- tables first,
then figures, then anything the document declared for itself under
`crossref.custom`. Each stands under a heading of its own, `LIST OF TABLES`
and the rest, with two column labels over the entries: what the list is of at
the left margin and `Page` at the right. An entry is the float's number, its
caption, leader dots and the page.

An illustration is a figure with a word and a count of its own, so it is
numbered from one rather than continuing after the figures, and its caption
is set the way a figure's is: the number on a line of its own with the
caption under it. `apa-note` works on it as it does on a figure, written
either on the image or on the div that holds it, and in .docx it is given the
same styles a figure has, which hold the note on the page with the
illustration it belongs to. The same goes for any other kind of float a
document declares.

``` yaml
format:
  apaquarto-pdf:
    crossref:
      custom:
        - kind: float
          reference-prefix: Illustration
          key: ill
          latex-env: illustration
```

Declare a custom float **in each format block** rather than once for all of
them. Quarto drops `latex-env` on the way through an extension's shared
options, and its own LaTeX code then stops on the missing field.

The lists are listed in the table of contents, as the handbook asks, and are
numbered in the same lower-case roman as the rest of the front matter.

## Line spacing

The handbook sets the line spacing part by part, and `documentmode: thesis`
follows it in all four formats.

The body is double spaced, and so are the abstract, the dedication, the
acknowledgments and the preface.

A block quotation is single spaced and indented half an inch from the left
margin *and* half an inch from the right, which is what marks it out as
quoted.

The entries of the reference list are single spaced within an entry, with a
double space between one entry and the next, hanging half an inch. The table
of contents and the lists of tables, figures and illustrations are set the
same way: a title of two or more lines is single spaced and turns over under
its own first word, and a double space stands between one entry and the next.

Notes are single spaced within a note, with a double space between one note
and the next and the first line indented half an inch, which is where the
note's number sits. In .html the number belongs to the list the browser draws
and is left where it is; the line spacing is the same.

Widows and orphans are avoided, so no page breaks after the first line of a
paragraph or before its last. The .pdf is the one that has to be told; .docx
and typst avoid them already, and .html has no pages to break.

Each format takes its own single spacing --- what Word, LaTeX and typst each
call a single-spaced line differs by a point or so --- and its own double,
which is what every other `documentmode` does too.

## Page numbering

The handbook asks for lower-case roman numerals through the front matter and
arabic numerals from the first page of the body, and says that "the Title
Page is page i, but does not show a page number". That is what
`documentmode: thesis` sets: the title page is counted and carries nothing,
the copyright page is ii, and the body begins again at 1.

There is no running head. The number sits at the centre of the foot, which is
where the dissertations Temple publishes put it.

Confirm the current requirements with the Graduate School before submitting:
apaquarto follows the 2024--2025 handbook, and a handbook is revised.

## The words of the front matter

Every word the front matter sets can be changed under `language`, for a
dissertation written in another language or a degree that words things
differently. A word left out keeps its English default.

``` yaml
language:
  thesis-committee: "Dissertation Committee:"
  thesis-list-of-illustrations: "LIST OF PLATES"
```

```{r}
#| echo: false
#| results: asis
apa_options("language-thesis")
```

# Tables of contents, figures, and tables

Each of these stands on a page of its own, after the abstract, the impact statement, the keywords and the supplemental materials, and before the body of the paper.

```{r}
#| echo: false
#| results: asis
apa_options("contents")
```

`list-of-figures` and `list-of-tables` are for .docx, typst and the .pdf; an entry in either reads `Figure 1. The Figure Caption`, with a leader out to the page number. Neither is built for .html, which has no pages to find.

In .docx those page numbers are fields, since nothing before Word lays the pages out knows what they are. They are blank when the file is opened and fill in correctly as soon as anything makes Word paginate: select all and press <kbd>F9</kbd>, or print, or export to pdf. Rendering says as much.

``` yaml
format:
  apaquarto-docx:
    list-of-contents: true
    list-of-figures: true
    list-of-tables: true
```

# The Colour a Link Takes

Quarto's five colour fields are LaTeX's, and apaquarto answers to all of them in all four formats.

```{r}
#| echo: false
#| results: asis
apa_options("link-colours")
```

A colour is named the way LaTeX names it --- one of the colours `xcolor` defines out of the box, or an HTML code:

``` yaml
linkcolor: "#cc0000"
urlcolor: green
citecolor: orange
filecolor: violet
toccolor: teal
```

`xcolor`'s table is what resolves a name, in every format, so `green` is the same green in the .docx, the .html, the typst and the .pdf. It is not always the green a browser means by that word: CSS `green` is `#008000` where `xcolor`'s is `#00FF00`. Write the code rather than the name to be sure of the shade.

Left unset, each link color defaults to `#0074D9`.

# Options for .html

With one exception, everything that works for .docx should work for .html. For .html, there is no benefit to having line numbers in the text because the text wrapping differs depending on the device and size of the window the document is being viewed.

# The Introduction Heading

APA does not label the introduction. The title of the paper stands at the top of the first page of text and the introduction runs on underneath it, so a heading reading *Introduction* is one heading too many.

apaquarto takes such a heading out for you. If the first heading in the body is a level-one heading whose text is *Introduction*, it is removed and the text under it is left where it is. A heading called *Introduction* anywhere else --- inside an appendix, say --- is left alone, as is one at any other level.

This matters most when the abstract is written as a section of the document, since something has to mark where the abstract ends and a heading is the obvious thing to reach for:

``` markdown
# Abstract

The abstract goes here.

# Introduction

The body of the paper starts here, and the heading above it does not
appear in the output.
```

The word it looks for is `section-title-introduction` in the `language` field, so a paper written in another language is matched too. To keep the heading, set `keep-introduction-heading: true`.

# Suppress Elements

Any of the elements below can be selectively suppressed from the document by setting the field to `true`.

```{r}
#| echo: false
#| results: asis
apa_options("suppress")
```

# Language Options

You can alter the names of Abstract, Figures, Tables, and References by setting the `lang` field to one of these languages:

:::: grid
::: {g-col-6}
| Code | Language   |
|------|------------|
| `en` | English    |
| `zh` | Chinese    |
| `es` | Spanish    |
| `fr` | French     |
| `ja` | Japanese   |
| `de` | German     |
| `pt` | Portuguese |
| `ru` | Russian    |
| `cs` | Czech      |
| `fi` | Finnish    |
| `nl` | Dutch      |
| `it` | Italian    |
| `pl` | Polish     |
| `ko` | Korean     |
:::
::::

However, there are a few options that are specific to apaquarto and thus were not anticipated by Quarto.

```{r}
#| echo: false
#| results: asis
apa_options("language-apaquarto")
```

All these options must be listed under the `language` field . For example, if we set the `lang` field to `es` (Spanish), the remaining options can also be set:

``` yaml
lang: es
language: 
  citation-last-author-separator: "y"
  citation-masked-author: "Cita Enmascarada"
  citation-masked-title: "Título Enmascarado"
  citation-masked-date: "n.f."
  title-block-author-note: "Nota de Autores"
  title-block-correspondence-note: "La correspondencia relativa a este artículo debe dirigirse a"
  title-block-role-introduction: "Los roles de autor se clasificaron utilizando la taxonomía de roles de colaborador (CRediT; https://credit.niso.org/) de la siguiente manera:"
  references-meta-analysis: "Las referencias marcadas con un asterisco indican estudios incluidos en el metanálisis."
  title-impact-statement: "Declaración de Impacto"
  title-word-count: "Recuento de Palabras"
```

In addition, many terms that are translated automatically can be overridden. The full list is [here](https://github.com/quarto-dev/quarto-cli/blob/main/src/resources/language/_language.yml). For example, if I wanted "Figure" in figure captions to be "Plot" instead, I would specify the change like so:

``` yaml
language: 
  crossref-fig-title: "Plot"
```

Here are the language terms most likely to be used in apaquarto:

```{r}
#| echo: false
#| results: asis
apa_options("language-quarto")
```
