---
title: "Using Quarto to Generate MS Word Documents in APA Style (7th Edition)"
blank-lines-above-title: 2
# If blank, the running header is the title in upper case.
runningheader: Template for the APAquarto Format
# Set names and affilations.
# It is nice to specify everyone's orcid, if possible.
# There can be only one corresponding author.
author:
  - name: Ana Fulana
    corresponding: true
    orcid: 0000-0000-0000-0000
    email: sm@example.org
    url: https://example.org/
    affiliations:
      - name: Ana and Blanca's University
        department: Department of Psychology
        address: 1234 Capital St.
        city: Albany
        region: NY
        postal-code: 12084-1234
      - name: Ana's Secondary Affiliation
  - name: Blanca Zutana
    affiliations: 
      - name: Ana and Blanca's University
        department: Department of Psychology
  - name: Carina Mengana
    orcid: 0000-0000-0000-0001
    affiliations:
      - name: Carina's Primary Affiliation
      - name: Carina's Secondary Affiliation
    # Because Dolorita is unaffiliated, specify her city instead
  - name: Dolorita Perengana
    orcid: 0000-0000-0000-0003
    affiliations:
      - name: ~
        city: Buffalo
        region: NY
author-note:
  blank-lines-above-author-note: 3
  status-changes:
    # Example: [Author name] is now at [affiliation].
    affilation-change: ~
    # Example: [Author name] is deceased.
    deceased: ~
  # Disclosures condensed to one paragraph, but you can start a field with two line breaks to break them up: \n\nNew Paragraph
  disclosures:
    # Example: This study was registered at ClinicalTrials.gov (Identifier NTC998877).
    study-registration: ~
    # Acknowledge and cite data/materials to be shared.
    data-sharing: ~
    # Example: This article is based on data published in Pulaski (2017).
    # Example: This article is based on the dissertation completed by Graham (2018).
    related-report: ~ 
    # Example: Sally Jones earns royalties from the sale of Test X.
    conflict-of-interest: ~
    # Example: This study was supported by Grant A123 from the National Science Foundation.
    financial-support: ~
    # Example: The authors are grateful for the technical assistance of Dr. X during the initial design and setup of our lab equipment.
    gratitude: ~
    # Example. Because the authors are equal contributors, order of authorship was determined by a fair coin toss.
    authorship-agreements: ~
abstract: |
  This document is a template demonstrating the apaquarto format.
keywords: [keyword, other keyword]
# I like using Zotero with BetterBibTeX to output a continuously updated "Better CSL JSON" file. But BibTeX works, too.
bibliography: bibliography.bib
format:
  apaquarto-docx: default
  native: default
---

{{< include _extensions/apaquarto/_apa_title.qmd >}}

This is my introductory paragraph. The title will be placed above it automatically. *Do not start with an introductory heading* (e.g., "Introduction"). The title acts as your Level 1 heading for the introduction.

Readers are better able to follow your ideas if you differentiate sections in your introduction with headings. Mostly stick to level 2 headers. Sometimes level 3 heading are needed. Try not to use a level 3 heading Be sparing to the point of stinginess with levels 4 and 5. 

## Level 2 Heading: Flush Left, Bold, Title Case

Subsections of the introduction have level 2 headings. A paragraph after a level 2 Heading is on a new line. Regular paragraphs are indented, flush left, and double-spaced.

You do not need to put text after a heading. You can put higher-level heading directly underneath if you want.

## A Level 2 Heading Without Text Below It

### Level 3 Heading: Flush Left, Bold Italic, Title Case

Subsections of a level 2 heading are placed under level 3 headings.

### Another Level 3 Heading

#### Level 4 Heading: Indented, Flush Left, Bold, Title Case, Ending With a Period.

A paragraph after a level 4 or 5 geading is on a new line in this markdown document but will appear as if it were in the same paragraph .docx format. You need at least one paragraph after a level 4 or 5 heading. If you forget the period at the end of the level 4 or 5 heading, it will be added automatically. A period will not be added if the heading ends with a question mark or an exclamation point.

Subsequent paragraphs go on their own lines.

##### Level 5 Heading: Indented, Flush Left, Bold Italic, Title Case, Ending With a Period

Notice that there was no period after this level 5 heading in the markdown document, but it does appear in the rendered document.

## How to Cite References

I am going to cite a reference here in square brackets [@CameronTrivedi2013]. This reference was in my bibliography file. Here are some variations on parenthetical citations:

* Page references (or any other suffixes are placed after the reference. If you want a comma, you'll need to insert it yourself: [@CameronTrivedi2013, pp. 35--41]

* Prefixes (with or without a comma) are placed before the reference: [e.g., @CameronTrivedi2013]

* 2 or more citations separated by a semicolon [@CameronTrivedi2013; @cohen2003applied]

* Any prefixes or suffixes needing a literal semicolon will confuse Quarto (actually Pandoc). To make it clear that you need to print a semicolon, put a backslash before the semicolon: [FOIL\; @CameronTrivedi2013]

Text references are possible, too. 

* @CameronTrivedi2013 said some interesting things. 

* @cohen2003applied [pp. 101--103] said specific things on specific pages.

* Place the reference's year by itself with a minus sign: [-@CameronTrivedi2013]

# Method

General remarks on method. This paragraph is optional.

## Participants

Who are they? How were they recruited? Perhaps some basic demographic stats are in order. A table is a great way to avoid repetition in statistical reporting.

## Measures (or Materials or Aparatus)

### Measure A

Describe Measure A.

### Measure B

Describe Measure B.

### Procedure

What did participants do?

### Analysis Plan 

How are the data going to be analyzed?

# Results

## Descriptive Statistics

Here we describe the basic characteristics of our primary variables.

Let's make a figure. A reference label for a figure in APA format must have the prefix `apafg-`. This is different from the usual quarto prefix `tbl-`, which will put the caption on one line below the table. For APA format, we can do this:

```{r}
#| label: apafg-myplot
#| apa-cap: This is the figure caption.
#| apa-note: This is a note below the figure.
plot(1:10)
```

To refer to any figure or table, but the chunk label in curly braces. For example, see {apafg-myplot}. In {apafg-importedgraphic}, we import an image.


```{r}
#| label: apafg-importedgraphic
#| apa-cap: This is an imported graphic.
knitr::include_graphics("_extensions/apaquarto/ORCID-iD_icon-vector.svg")
```


We can make a table the same way as a figure except that the label prefix is `apatb-`. Again, this is different from the usual quarto prefix `tbl-`, which will put the table table caption in the wrong place and with non-APA formatting.

```{r apatb-mytable}
#| apa-cap: Here is the table caption.
#| apa-note: Here is the note below the table.
#| ft.align: left
library(tidyverse)
library(flextable)


tibble(Numbers = seq(1,4), Letters = LETTERS[seq(Numbers)]) %>% 
  flextable() %>% 
  theme_apa() %>% 
  line_spacing(part = "all") %>% 
  padding(padding.top = 5, padding.bottom = 5)

```

To refer to this table in text, put the table's reference label in curly braces like so: As seen in {apatb-mytable}, there is not much information.

What if you want the tables and figures to be at the end of the document? No problem. Just put them all at the end, in order. The reference labels will work no matter where they are in the text. In {apatb-myothertable}, I give an example of making a table at the end using markdown only. 

<!-- Add Additional Sections as Needed -->

# Discussion

Describe results in non-statistical terms.
<!-- Add sections as needed. --> 

## Limitations and Future Directions

Every study has limitations. Based on this study, some additional steps might include...

## Conclusion

Let's sum this up.

# References 

<!-- References will auto-populate in the refs div below -->

::: {#refs}

:::

<!-- Delete any unnecessary sections or pagebreaks. -->
{{< pagebreak >}}
# Appendix 

If there are multiple appendices, label them with level 1 headings as Appendix A, Appendix A, and so forth.


<!-- I like my tables and figures intermingled with the text, -->
<!-- but all tables can go here. -->
<!-- Uncomment the pagebreaks as needed-->
{{< pagebreak >}}

Here I show how to set up everything yourself in markdown instead of using a code chunk to generate the table.

<!-- Set the table reference label with the #apatb- prefix -->
::::{#apatb-myothertable}

<!-- The Table # will appear here -->
:::{.FigureTitle}
{apatb-myothertable}
:::

<!-- Set your caption here -->
:::{.Caption}
This a a table caption.
:::

<!-- Table goes here -->
<!-- Set class to .FigureWithoutNote if no note will appear below. -->
:::{.FigureWithNote}

Column 1 | Column 2
:--------|:-------:
A        | Yes
B        | No

:::

<!-- Make a note below the table -->
:::{.FigureNote}
*Note*. This is a table note.
:::
::::

<!-- Figures can go here. -->
<!-- {{< pagebreak >}} -->